### 2023-05-28 paper/Chapters/Chapter2.tex
Update the paper and the evaluation
2AM woo-hoo

Later, ArUco
~\citep{garrido-juradoAutomaticGenerationDetection2014} (\cref{fig:gboriginal}) and
AprilTag~\citep{olsonAprilTagRobustFlexible2011a} (\cref{fig:apriltag})
allowed detecting the
orientation of the pattern, as well as uniquely identifying each located pattern
even under occlusion. Based on ArUco,
ChArUcO~\citep{OpenCVCameraCalibration} (\cref{fig:charuco}) was
proposed as more robust.

@@

Nevertheless, camera calibration is still an open problem; recently,
multiple new approaches have arisen.
\cite{lochmanBabelCalibUniversalApproach2021} suggest a universal approach
to camera calibration, with a separate step of converting between camera models.
\cite{huDeepChArUcoDark2019} used deep learning to detect ChArUcO boards.
Recently, on \citedate{duisterhofTartanCalibIterativeWideAngle2022},
\cite{duisterhofTartanCalibIterativeWideAngle2022} introduced the iterative
approach to camera calibration, which outperforms the previous state-of-the-art
approaches for wide-angle cameras.

\todo{Add the paper about the feature detection}

@@

Because of that, other methods were proposed, such as
\cite{fuersattelOCPADOccludedCheckerboard2016} and
\cite{geigerAutomaticCameraRange2012}. Those method can detect the board under
the partial occlusion and do not require prior knowledge of the board's geometry.

>>>>

Later, ArUco
~\citep{garrido-juradoAutomaticGenerationDetection2014} (\cref{fig:gboriginal}) and
AprilTag~\citep{olsonAprilTagRobustFlexible2011} (\cref{fig:apriltag})
allowed detecting the
orientation of the pattern, as well as uniquely identifying each located pattern
even under occlusion. Based on ArUco,
ChArUcO~\citep{OpenCVCameraCalibration} (\cref{fig:charuco}) was
proposed as more robust.

@@

Nevertheless, camera calibration is still an open problem; recently,
multiple new approaches have arisen.
\cite{scaramuzzaToolboxEasilyCalibrating2006} proposed an automatic algorithm
for camera calibration, which did not use any model of the specific omnidirectional
sensor.
\cite{lochmanBabelCalibUniversalApproach2021} suggest a universal approach
to camera calibration, with a separate step of converting between camera models.
\cite{huDeepChArUcoDark2019} used deep learning to detect ChArUcO boards.
Recently, on \citedate{duisterhofTartanCalibIterativeWideAngle2022},
\cite{duisterhofTartanCalibIterativeWideAngle2022} introduced the iterative
approach to camera calibration, which outperforms the previous state-of-the-art
approaches for wide-angle cameras.

@@

Because of that, other methods were proposed, such as
\cite{fuersattelOCPADOccludedCheckerboard2016} and
\cite{geigerAutomaticCameraRange2012}. Those method can detect the board and
associate the corners with the borders' corners under
the partial occlusion and do not require prior knowledge of the board's geometry.

\cite{chenNewSubPixelDetector2005} proposed using Hessian to find pixel
positions of the corners.

### 2023-05-28 paper/Chapters/Chapter4.tex
2AM woo-hoo

For the feature detection, we used the approach proposed by
\cite{geigerAutomaticCameraRange2012} (see \cref{sec:boards_features_detection,
	feature_detection}).
\missingfigure{Show the feature detection results.}

@@

In this work, we obtained the camera calibration in two steps: first, we
used the approach, proposed by \cite{scaramuzzaToolboxEasilyCalibrating2006} to
obtain the initial approximation of the camera parameters. Then, we used the
optimization to minimize the reprojection error between the board and the
back-projected corners.

@@

Let's define the following variables: \(\boldsymbol{\theta} = \begin{pmatrix}
	\theta_x, \theta_y, \theta_z
\end{pmatrix}^{T}\) is the vector of Euler rotation angles, \(\mathbf{t} = \begin{pmatrix}
	t_x, t_y, t_z
\end{pmatrix}^{T}\) is the translation vector, \(\boldsymbol{\lambda} = \begin{pmatrix}
	\lambda_1, \lambda_2
\end{pmatrix}^{T}\)\todo{Justify why we used 2} is the intrinsic parameters vector, \(\) is the focal
length, and \(\mathbf{s} = \begin{pmatrix}
	s_x, s_y
\end{pmatrix}^{T}\) is the sensor size\todo{Make sure I'm using the correct terms.}.
From the input image, we know the resolution \(\mathbf{r} = \begin{pmatrix}
	r_x, r_y
\end{pmatrix}^{T}\).
From the rotation vector, we can compute the rotation matrix \(\mathbf{R}\) as:

@@

\missingfigure{Show the distribution of the reprojection error}.

@@

\missingfigure{Show the image, the respective board, and the imputed points}

@@

In this work, we used the method, proposed by
\cite{geigerAutomaticCameraRange2012} as it didn't require the whole board to be
visible, automatically determines the board's number of rows and columns and
worked quite well on highly-distorted images.

@@

\subsection{Sub-pixel Corner and Orientation Refinement}\label{sub:sub_pixel_corner_and_orientation_refinement}

Sub-pixel accurate corner locations and edge orientations are refined using the following optimizations:

For sub-pixel corner localization, the corner $\mathbf{c}$ in a 2D space
$\mathbb{R}^2$ is refined using the assumption that the gradient direction
\(\mathbf{g_{p}}\) at
each pixel  \(\mathbf{p}\) in the small neighbourhood around the corner is
orthogonal to \(\mathbf{p} - \mathbf{c}\).

\begin{equation}
	\mathbf{c}=\arg \min _{\mathbf{c}^{\prime}} \sum_{\mathbf{p} \in
	\mathcal{N}_{\mathbf{I}}\left(\mathbf{c}^{\prime}\right)}\left(\mathbf{g}_{\mathbf{p}}^T\left(\mathbf{p}-\mathbf{c}^{\prime}\right)\right)^2
\end{equation}

For the orientation refinement, authors minimize the distance from the
orientation vectors \(\mathbf{e_1}, \mathbf{e_2}\) to the gradient directions
\(\mathbf{g_p}\) in the neighbourhood of the corner.

\begin{equation}
	\mathbf{e}_i=\arg \min _{\mathbf{e}_i^{\prime}} \sum_{\mathbf{p} \in
		\mathcal{M}_i}\left(\mathbf{g}_{\mathbf{p}}^T \mathbf{e}_i^{\prime}\right)^2
	\quad \text { s.t. } \mathbf{e}_i^{\prime T} \mathbf{e}_i^{\prime}=1
\end{equation}.

The original paper then used a number of checks to further prune the detected
corners, and extending line by line the initial board, formed from the
random close points which made a square \todo{Make sure that's accurate, and
	reference. Also, the sentence is too compicated}.
We did not require that, since we already had the board, and we directly used
the response map to find the corners.

\missingfigure{Show the map of responses, and the detected corners}

To create a training dataset, we collected the true and false positives from the
corners we already had:

For each of the detected corners on all images, we collected the values of the
response function at the previously detected corners, and around them.
We didn't collect the values of all of the pixels, because then we would have
got too optimistic values for selecting the true positives\todo{Rephrase}.

\missingfigure{Show the distribution of the response function}

We trained a binary classifier, using the collected data, and then used it to
detect the true corners.

>>>>

For the feature detection, we used the approach, proposed by
\cite{geigerAutomaticCameraRange2012} (see \cref{sec:boards_features_detection,
	sec:feature_detection}).

@@

In this work, we obtained the camera calibration in two steps: first, we
used the approach, proposed by \cite{scaramuzzaToolboxEasilyCalibrating2006} to
obtain the initial approximation of the camera parameters. Then, we used the
optimization to minimize the reprojection error between the board and the
back-projected corners. A division model is very powerful, and is able to
express a wide number of range of distortions
\citep{prittsMinimalSolversRectifying2021}. In this work, we used a model with
two parameters to allow for a better flexibility during the optimization.

@@

Let's define the following variables: \(\boldsymbol{\theta} = \begin{pmatrix}
	\theta_x, \theta_y, \theta_z
\end{pmatrix}^{T}\) is the vector of Euler rotation angles, \(\mathbf{t} = \begin{pmatrix}
	t_x, t_y, t_z
\end{pmatrix}^{T}\) is the translation vector, \(\boldsymbol{\lambda} = \begin{pmatrix}
	\lambda_1, \lambda_2
\end{pmatrix}^{T}\) is the intrinsic parameters vector, \(\) is the focal
length, and \(\mathbf{s} = \begin{pmatrix}
	s_x, s_y
\end{pmatrix}^{T}\) is the sensor size.
From the input image, we know the resolution \(\mathbf{r} = \begin{pmatrix}
	r_x, r_y
\end{pmatrix}^{T}\).
From the rotation vector, we can compute the rotation matrix \(\mathbf{R}\) as:

@@

@@

@@

In this work, one of the methods we used was proposed by
\cite{geigerAutomaticCameraRange2012} as it didn't require the whole board to be
visible, automatically determines the board's number of rows and columns and
worked quite well on highly-distorted images.

@@

% \subsection{Sub-pixel Corner and Orientation Refinement}\label{sub:sub_pixel_corner_and_orientation_refinement}
%
% Sub-pixel accurate corner locations and edge orientations are refined using the following optimizations:
%
% For sub-pixel corner localization, the corner $\mathbf{c}$ in a 2D space
% $\mathbb{R}^2$ is refined using the assumption that the gradient direction
% \(\mathbf{g_{p}}\) at
% each pixel  \(\mathbf{p}\) in the small neighbourhood around the corner is
% orthogonal to \(\mathbf{p} - \mathbf{c}\).
%
% \begin{equation}
% 	\mathbf{c}=\arg \min _{\mathbf{c}^{\prime}} \sum_{\mathbf{p} \in
% 	\mathcal{N}_{\mathbf{I}}\left(\mathbf{c}^{\prime}\right)}\left(\mathbf{g}_{\mathbf{p}}^T\left(\mathbf{p}-\mathbf{c}^{\prime}\right)\right)^2
% \end{equation}
%
% For the orientation refinement, authors minimize the distance from the
% orientation vectors \(\mathbf{e_1}, \mathbf{e_2}\) to the gradient directions
% \(\mathbf{g_p}\) in the neighbourhood of the corner.
%
% \begin{equation}
% 	\mathbf{e}_i=\arg \min _{\mathbf{e}_i^{\prime}} \sum_{\mathbf{p} \in
% 		\mathcal{M}_i}\left(\mathbf{g}_{\mathbf{p}}^T \mathbf{e}_i^{\prime}\right)^2
% 	\quad \text { s.t. } \mathbf{e}_i^{\prime T} \mathbf{e}_i^{\prime}=1
% \end{equation}.

\subsection{Classifier training}\label{sub:classifier_training}

We tested the approach of \cite{geigerAutomaticCameraRange2012}, and,
alternatively, the Hessian responses for the image, as proposed by
\cite{chenNewSubPixelDetector2005}.

To create a training dataset, we collected the true and false positives from the
corners we already detected.

For each of the detected corners on all images, we collected the values of the
response function at the previously detected corners, and around them.
We didn't collect the values of all of the pixels, in order to reduce the number
of very simple examples.

To determine the threshold for the classification, we used the ROC curve, and
found the threshold which maximizes
the geometric mean of the true positive rate and the false positive rate.

We used both of the approaches to train the classifier, and compared the
results in \cref{sec:classification}.

### 2023-05-28 paper/Chapters/Chapter5.tex
2AM woo-hoo

We created a symulator to generate distorted points. We used it to test the
solver, and test the correctness of projection and back-projection points.

@@

@@

\textbf{Kalibr} contains several established datasets that are commonly used for testing
the accuracy of camera calibration frameworks: Double Sphere
\cite{usenkoDoubleSphereCamera2018}, EuRoC \cite{burriEuRoCMicroAerial2016}, TUM
VI \cite{schubertTUMVIBenchmark2018}, and ENTANIYA 1
\cite{Calibration250degFisheye}.
The Kalibr calibration framework was used in the
original publications cited above, hence the name of the dataset.
As a calibration pattern, AprilGrid with 6x6 tags of 88 mm size was used.
In total, the datasets contain approximately 800 images.

\textbf{OCamCalib} \cite{scaramuzzaFlexibleTechniqueAccurate2006} is a dataset
of approximately 300 images.
As a calibration pattern, the checkerboard pattern of different sizes was used.

\textbf{UZH} \cite{AreWeReady} is a dataset of approximately 800 images
collected using the following cameras:
As a calibration pattern, AprilGrid with 4x5 tags of 75 mm size was used.
The dataset contains approximately 800 images.

\textbf{OV} \cite{duisterhofTartanCalibIterativeWideAngle2022} is a dataset of
approximately 1400 images. It was collected using eight stereo cameras.
As a calibration pattern, the checkerboard pattern with 9x6 tags of 22 mm size
was used.

\textcite{duisterhofTartanCalibIterativeWideAngle2022} also provide their
dataset from the TartanCalib project, but it is quite challenging to use it as it
comes in the Robot Operating System (ROS) .bag format.

\begin{figure}[h!]
	\centering
	\begin{subfigure}[b]{0.3\linewidth}
		\includegraphics[width=\linewidth]{Kalibr.png}
		\caption{Kalibr}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.3\linewidth}
		\includegraphics[width=\linewidth]{OCamCalib.png}
		\caption{OCamCalib}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.3\linewidth}
		\includegraphics[width=\linewidth]{OV.png}
		\caption{OV}
	\end{subfigure}
	\begin{subfigure}[b]{0.3\linewidth}
		\includegraphics[width=\linewidth]{UZH.png}
		\caption{UZH}
	\end{subfigure}
	\begin{subfigure}[b]{0.3\linewidth}
		\includegraphics[width=\linewidth]{tartancalib.png}
		\caption{TartanCalib}
	\end{subfigure}
	\caption{Images from the datasets}
\end{figure}

\todo{Probably, remove everything but BabelCalib, as we didn't use AprilGrid}

>>>>

We created a symulator to generate distorted points as described in
\cref{sub:complete_projection_and_backprojection}. We used it to test the
solver, and test the correctness of projection and back-projection points.

@@

For this project, we required a highly distorted dataset of chessboard images.
We collected a number of datasets, but the feature detector we used supports
detecting only the boards with the constant tile size, therefore we cannot use
AprilGrid nor CharuCO boards. The feature detector is the only limiting factor.

@@

\textbf{Kalibr} \citep{mayeSelfsupervisedCalibrationRobotic2013} contains several established datasets that are commonly used for testing
the accuracy of camera calibration frameworks: Double Sphere
\cite{usenkoDoubleSphereCamera2018}, EuRoC \cite{burriEuRoCMicroAerial2016}, TUM
VI \cite{schubertTUMVIBenchmark2018}, and ENTANIYA 1
\cite{Calibration250degFisheye}.
The Kalibr calibration framework was used in the
original publications cited above, hence the name of the dataset.
As a calibration pattern, AprilGrid with 6x6 tags of 88 mm size was used.
In total, the datasets contain approximately 800 images.

\textbf{OCamCalib} \citep{scaramuzzaFlexibleTechniqueAccurate2006} is a dataset
of approximately 300 images.
As a calibration pattern, the checkerboard pattern of different sizes was used.

\textbf{UZH} \citep{AreWeReady} is a dataset of approximately 800 images
collected using the following cameras:
As a calibration pattern, AprilGrid with 4x5 tags of 75 mm size was used.
The dataset contains approximately 800 images.

\textbf{OV} \citep{lochmanBabelCalibUniversalApproach2021} is a dataset of
approximately 1400 images. It was collected using eight stereo cameras.
As a calibration pattern, the checkerboard pattern with 9x6 tags of 22 mm size
was used.

\textcite{duisterhofTartanCalibIterativeWideAngle2022} also provide their
dataset from the TartanCalib project. Currently, the dataset contains only
AprilGrid patterns, as the toolchain doesn't support chessboard.

\begin{figure}[h]
	\centering
	\begin{subfigure}[b]{0.3\linewidth}
		\includegraphics[width=\linewidth]{Kalibr.png}
		\caption{Kalibr}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.3\linewidth}
		\includegraphics[width=\linewidth]{OCamCalib.png}
		\caption{\textbf{OCamCalib}}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.3\linewidth}
		\includegraphics[width=\linewidth]{OV.png}
		\caption{\textbf{OV}}
	\end{subfigure}
	\begin{subfigure}[b]{0.3\linewidth}
		\includegraphics[width=\linewidth]{UZH.png}
		\caption{UZH}
	\end{subfigure}
	\begin{subfigure}[b]{0.3\linewidth}
		\includegraphics[width=\linewidth]{tartancalib.png}
		\caption{TartanCalib}
	\end{subfigure}
	\caption{Images from the datasets}
\end{figure}

\section{Camera calibration}\label{sec:camera_calibration}

\begin{minipage}{0.5\linewidth}
	In order to get accurate predictions for the possibly missing points, we need
	very accurate camera calibration. We used the reprojection error as a metric
	for the calibration quality.
	In order to calculate the reprojection error, we have to perform the
	rootfinding \cref{subsub:back_projection_using_the_division_model}. We assume
	that all of the points lay within the image, or they get out of the borders
	a little bit (we use the constant \(1.1\) of the maximum radius). If the
	camera calibration is poor, the rootfinding might fail. On the initial
	calibration the number of the failed rootfindings was much higher.
\end{minipage}
\hfill
\begin{minipage}{0.4\linewidth}
	\resizebox{\linewidth}{!}{
		\begin{tikzpicture}
			\pie[rotate=90, explode=0.1, sum=auto, color={green!60, blue!60, red!60}, text=legend]{
				115/Correctly detected,
				80/Reprojection error > 10,
				254/Not correctly detected
			}
		\end{tikzpicture}
	}
	\captionsetup{width=.9\linewidth}
	\captionof{figure}{Initial calibration}
	\resizebox{\linewidth}{!}{
		\begin{tikzpicture}
			\pie[rotate=90, explode=0.1, sum=auto, color={green!60, blue!60, red!60}, text=legend]{
				658/Correctly detected,
				19/Reprojection error > 10,
				115/Not correctly detected
			}
		\end{tikzpicture}
	}
	\captionsetup{width=.9\linewidth}
	\captionof{figure}{Final calibration}
\end{minipage}

\begin{figure}[h]
	\begin{tikzpicture}
		\begin{axis}[
				ybar interval,
				ymin=0,
				ylabel={Frequency},
				xlabel={Value},
				height=0.3\linewidth,
				width=\linewidth,
				ticklabel style = {font=\tiny},
				% title={Initial calibration}
			]
			\addplot+ [hist={data min=0,data max=10,bins=20}] table [y index=0]
				% \addplot+ [hist={bins=30}] table [y index=0]
				{data/reprojection_error_init.txt};
		\end{axis}
	\end{tikzpicture}
	\caption{Initial calibration's reprojection error histogram}
\end{figure}
\begin{figure}[h]
	\begin{tikzpicture}
		\begin{axis}[
				ybar interval,
				ymin=0,
				ylabel={Frequency},
				xlabel={Value},
				height=0.3\linewidth,
				width=\linewidth,
				ticklabel style = {font=\tiny},
				% title={Reprojection error}
			]
			\addplot+ [hist={data min=0,data max=10,bins=20}] table [y index=0]
				% \addplot+ [hist={bins=30}] table [y index=0]
				{data/reprojection_error_final.txt};
		\end{axis}
	\end{tikzpicture}
	\caption{Final calibration's reprojection error histogram}
\end{figure}

\section{Additional features detection}\label{sec:additional_features_detection}

As discussed in \cref{sec:additional_features_detection}, we filled the gaps in
the originally detected board points, and then padded it for 1 additional
element.

\begin{figure}[h]
	\centering
	\begin{minipage}{0.55\linewidth}
		\begin{subfigure}[b]{\linewidth}
			\includegraphics[width=\linewidth]{extended_board_img.png}
			\label{fig:extended_board_img}
			\caption{Extended board, new points are marked as blue}
		\end{subfigure}
	\end{minipage}
	\begin{minipage}{0.35\linewidth}
		\resizebox{\linewidth}{!}{
			\begin{tikzpicture}
				\begin{axis}[
						xlabel={$x$},
						ylabel={$y$},
						grid=major,
						title={Original board},
					]
					\addplot[
						only marks,
					] table {data/original_board.txt};
				\end{axis}
			\end{tikzpicture}
		}
		\vfill
		\resizebox{\linewidth}{!}{
			\centering
			\begin{tikzpicture}
				\begin{axis}[
						xlabel={$x$},
						ylabel={$y$},
						grid=major,
						title={Extended board},
					]
					\addplot[
						only marks,
					] table {data/extended_board.txt};
				\end{axis}
			\end{tikzpicture}
		}
	\end{minipage}
	\caption{Board extension}
\end{figure}

\section{Classification}\label{sec:classification}

\begin{minipage}[t]{0.3\linewidth}
	We compared both responses, as discussed in \cref{sec:classifier}.
	The Hessian proved to be more robust. The approach, proposed by
	\cite{geigerAutomaticCameraRange2012} gave too many false positives,
	especially for the edges.
\end{minipage}
\hfill
\begin{minipage}[t]{0.6\linewidth}
	\includegraphics[width=\linewidth]{response_hessian.png}
	\captionof{figure}{Hessian response}
	\includegraphics[width=\linewidth]{response_other.png}
	\captionof{figure}{Response used by \cite{geigerAutomaticCameraRange2012}}
	% \end{figure}
\end{minipage}

\begin{figure}
	\centering
	\begin{subfigure}[t]{\linewidth}
		\includegraphics[width=\linewidth]{hist_response_hessian.png}
		\caption{Histogram of Hessian response}
	\end{subfigure}
	\begin{subfigure}[t]{\linewidth}
		\includegraphics[width=\linewidth]{hist_response_other.png}
		\caption{Histogram of response used by \cite{geigerAutomaticCameraRange2012}}
	\end{subfigure}
	\caption{Distributions of the responses for the image on the
		\cref{fig:extended_board_img}. Note the log y-scale! Most of the points have
		the response 0.}
\end{figure}

\section{Evaluation}\label{sec:evaluation}

\missingfigure{Compare the number of points with the provided by babelcalib}
\missingfigure{Compare the reprojection error}

### 2023-05-28 paper/paper.tex
OMG it's horrible
WIP
Update the paper and the evaluation
2AM woo-hoo

\usepackage[textwidth=20mm]{todonotes}
\setlength{\marginparwidth}{2.5cm}
\usepackage{caption}
\usepackage{subcaption}
\graphicspath{ {images/} }

@@

\begin{abstract}
	\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
	The Thesis Abstract is written here (and usually kept to just this page). The page is kept centered vertically so can expand into the blank space above the title too\ldots

	Camera calibration is a crucial step in many computer vision applications.
  Typically, it involves taking a set of images of a calibration pattern,
  detecting its' features, and estimating the camera parameters. However, under
  certain conditions (including occlusions, bad lightning, highly distorted
  images etc.), feature detectors might fail to detect some of the
  features.\todo{Do I have to justify it?}.

  In this paper, we propose a novel approach to feature detection in the context
  of camera calibration. After the initial feature detection and calibration,
  we use the intermediate camera parameters to predict the possible positions
  of the previously undetected features. Those features are filtered using the
  binary classifier, and the remaining features are used to further constrain
  the camera calibration.

@@

\include{Chapters/Chapter1}
\include{Chapters/Chapter2} 
\include{Chapters/Chapter3}
\include{Chapters/Chapter4} 
\include{Chapters/Chapter5} 
\include{Chapters/Chapter6}

>>>>

\usepackage[textwidth=20mm]{todonotes}
\setlength{\marginparwidth}{2.5cm}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{cleveref}
\usepackage{xfrac}
\usepackage{multicol}
\usepackage{float}
\usepackage{cases}
\usepackage{pgfplots}
\usepackage{pgf-pie}
\graphicspath{ {images/} }

@@

\begin{abstract}
	\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
	% The Thesis Abstract is written here (and usually kept to just this page). The page is kept centered vertically so can expand into the blank space above the title too\ldots

	Current state-of-the-art techniques occasionally fail to accurately estimate
	the camera parameters for wide-angle lenses, as most of the algorithms assume
	lens with medium to small distortion. Partially it occurs due to extreme
	distortion at the edges of the image, which poses additional challenges to
	feature detection algorithms. We propose a novel approach for detecting
	additional features on the imaged calibration pattern using intermediate
	camera calibration. Utilizing the prior information about the calibration
	pattern's geometry, we can estimate the possible positions of the previously
	undetected features. Those features are filtered using the binary classifier,
	and the remaining ones are used to further constrain the camera calibration.
	The proposed method consists of three key steps: \((1)\) feature
	detection and estimation of the lattice geometry, \((2)\) initial camera
	calibration by solving the two-steps linear minimization problem, and \((3)\)
	estimation the possible positions of the undetected features by projecting the
	imputed and extended lattice geometry onto the image plane, and filtering them
	using the binary classifier.

@@

\include{Chapters/Plan}
\include{Chapters/Chapter1}
\include{Chapters/Chapter2}
\include{Chapters/Chapter3}
\include{Chapters/Chapter4}
\include{Chapters/Chapter5}
\include{Chapters/Chapter6}
